Figures and Tables

### 2021-02-03 paper/figures_tables.Rmd
include legend to density

#scale
b <- 1
kappaexp <- b^-exptail
kappathin <- b^-thintail
kappafat <- b^-fattail

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
                color = "black", linetype = "dashed", size = 0.8) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
                color = "black", linetype = "dotted", size = 0.8) +
  stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
                color = "black", linetype = "solid", size = 0.8) +
  ylab("") + xlab("") +
  lims(y = c(0, 1)) +
  theme_bw() -> weib_dens

@@

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = betatail, type = "GP"),
                color = "black", linetype = "dashed", size = 0.8) +
  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = exptail, type = "GP"), 
                color = "black", linetype = "dotted", size = 0.8) +
  stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = heavytail, type = "GP"),
                color = "black", linetype = "solid", size = 0.8) +
  ylab("") + xlab("") +
  lims(y = c(0, 1)) +
  theme_bw() -> gp_dens

>>>>

#scale
b <- 1
kappaexp <- b^-exptail
kappathin <- b^-thintail
kappafat <- b^-fattail
# 
# ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
#   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = thintail),
#                 color = "black", linetype = "dashed", size = 0.8) +
#   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = exptail), 
#                 color = "black", linetype = "dotted", size = 0.8) +
#   stat_function(fun = dweibull, n = 100, args = list(scale = b, shape = fattail),
#                 color = "black", linetype = "solid", size = 0.8) +
#   ylab("") + xlab("") +
#   lims(y = c(0, 1)) +
#   theme_bw() -> weib_dens

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(aes(linetype = "Thin tail"), fun = dweibull, n = 100, args = list(scale = b, shape = thintail)) +
  stat_function(aes(linetype = "Exponential"), fun = dweibull, n = 100, args = list(scale = b, shape = exptail)) +
  stat_function(aes(linetype = "Heavy tail"), fun = dweibull, n = 100, args = list(scale = b, shape = fattail)) +
  ylab("") + xlab("") +
  lims(y = c(0, 1)) +
  theme_bw() +
  theme(legend.position = c(0.7, 0.7),
        legend.title = element_blank()) -> weib_dens

@@

# ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
#   stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = betatail, type = "GP"),
#                 color = "black", linetype = "dashed", size = 0.8) +
#   stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = exptail, type = "GP"), 
#                 color = "black", linetype = "dotted", size = 0.8) +
#   stat_function(fun = devd, n = 100, args = list(scale = gp_scale, shape = heavytail, type = "GP"),
#                 color = "black", linetype = "solid", size = 0.8) +
#   ylab("") + xlab("") +
#   lims(y = c(0, 1)) +
#   theme_bw() -> gp_dens

ggplot(data = data.frame(x = c(0.1, 4)), aes(x)) +
  stat_function(aes(linetype = "Beta"), fun = devd, n = 100, args = list(scale = gp_scale, shape = betatail, type = "GP")) +
  stat_function(aes(linetype = "Exponential"), fun = devd, n = 100, args = list(scale = gp_scale, shape = exptail, type = "GP")) +
  stat_function(aes(linetype = "Pareto"), fun = devd, n = 100, args = list(scale = gp_scale, shape = heavytail, type = "GP")) +
  ylab("") + xlab("") +
  lims(y = c(0, 1)) +
  theme_bw()  +
  theme(legend.position = c(0.7, 0.7),
        legend.title = element_blank()) -> gp_dens
